Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-19 snapshot_system/fast14_architecture.tex
update formula

\section{Architecture and Implementation Details}
\label{sect:architecture}
Our system runs on a cluster of Linux machines with Xen-based VMs.
A distributed file system (DFS) manages  the physical disk storage and we use 
an open source DFS called QFS~\cite{QFS}. 
All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).

>>>>

\section{Architecture and Implementation Details}
\label{sect:architecture}
Our system runs on a cluster of Linux machines with Xen-based VMs.
A distributed file system (DFS) manages the physical disk storage and we use 
an open source DFS called QFS~\cite{QFS}. 
% All data needed for VM services, such as virtual disk images used by runtime VMs,
% and snapshot data for backup purposes, reside in this distributed file system. 
All data needed for VM snapshot services, such as snapshot and segment recipes,
chunk data and PDS data are reside in this distributed file system. 
One physical node hosts tens of VMs, each of which accesses its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).

### 2013-09-19 snapshot_system/fast14_deduplication.tex
update formula

We use filesystem blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To  compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by this VM.

For VC, each VM has an average number of $N_1$ non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS file system block is associated with one VM
 and  we denote that PDS file system blocks are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Then, 
\[
V *p*N_1 *s  \approx c_u (1-\sigma)\; \mbox{ and } \; 
V *p*N_2 *s  \approx c_u \sigma *V_c
\]
For the VO approach, 
For VO, each VM has an average  of  $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each file system block.
\[
V *p*N_o *s  \approx c_u  V_o.
\]

@@

The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
 $N_2$ for VC and $N_o$ for VO.
With replication degree $r$, the availability of a file block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines. 
Namely, $1-\binom{d}{r}/ \binom{p}{r}$. 
The snapshot availability of a VM  in the VO approach is
\begin{equation}
\label{eq:VO}
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
\end{equation}

For VC, there are two cases for $d$ failed machines.
\begin{itemize}
\item
When $r \le d<r_c$,  there is no PDS data loss and  
the full snapshot availability of a VM in the VC approach is 
\[
(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\]
Since $N_1 <N_o$, the VC approach has a higher availability of VM snapshots than VO.

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\[
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\]
Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

>>>>

We use file system blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by this VM.

For VC, each VM has an average number of $N_1$ non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS file system block is associated with one VM
 and  we denote that PDS file system blocks are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Then, 
\[
V *p*N_1 *s  \approx c_u (1-\sigma)\; \mbox{ and } \; 
V *p*N_2 *s  \approx c_u \sigma *V_c
\]
For the VO approach, 
For VO, each VM has an average of $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each file system block.
\[
V *p*N_o *s  = c_u  V_o.
\]

@@

The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
 $N_2$ for VC and $N_o$ for VO.
Given normal data replication degree $r$, PDS data replication degree $r_c$, 
the availability of a file system block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
Namely, we define it as
\[
A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
\]
Then the availability of one VM's snapshot data under VO approach is the probability that
 all its file system blocks are unaffected during the system failure:
\begin{equation}
\label{eq:VO}
%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
A(r)^{N_o}. 
\end{equation}

For VC, there are two cases for $d$ failed machines.
\begin{itemize}
\item
When $r \le d<r_c$,  there is no PDS data loss and  
the full snapshot availability of a VM in the VC approach is 
\begin{equation}
\label{eq:VC1}
%(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
A(r)^{N_1}.
\end{equation}
Since $N_1$ is typically much smaller than $N_o$, 
the VC approach has a higher availability of VM snapshots than VO.

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\begin{equation}
\label{eq:VC2}
% (1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
% *
% (1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
A(r)^{N_1} * A(r_c)^{N_2}
\end{equation}
Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
with different replication degree. This demonstrates inequality 
% $1-\frac{ \binom{d}{r}} { \binom{p}{r} } < 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$
$A(r) < A(r_c)$
.  Since $N_1$ is much smaller than $N_o$ as discussed previously, 
these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}
